---
title: "R Notebook"
output: html_notebook
---

#1. Importing the Datasets
Dataset Link: https://drive.google.com/file/d/1CTAlmlREFRaEN3NoHHitewpqAtWS5cVQ/view
We are importing the datasets that contain transactions made by credit cards-

```{r}
library(lattice)
library(ggplot2)
library(ranger)
library(caret)
library(data.table)
creditcard_data <- read.csv("C:/Users/KIIT/Documents/5th Semester/AP Lab G2/Credit-card-dataset/creditcard.csv")
```

#2. Data Exploration
In this section of the fraud detection ML project, we will explore the data that is contained in the creditcard_data dataframe. We will proceed by displaying the credit card_data using the head() function as well as the tail() function. We will then proceed to explore the other components of this dataframe –
```{r}
dim(creditcard_data)
head(creditcard_data,6)
```

```{r}
tail(creditcard_data,6)
```

```{r}
table(creditcard_data$Class)
summary(creditcard_data$Amount)
names(creditcard_data)
var(creditcard_data$Amount)
```

```{r}
sd(creditcard_data$Amount)
```

#3. Data Manipulation
In this section of the R data science project, we will scale our data using the scale() function. We will apply this to the amount component of our creditcard_data amount. Scaling is also known as feature standardization. With the help of scaling, the data is structured according to a specified range. Therefore, there are no extreme values in our dataset that might interfere with the functioning of our model. We will carry this out as follows:
```{r}
head(creditcard_data)
```

```{r}
creditcard_data$Amount=scale(creditcard_data$Amount)
NewData=creditcard_data[,-c(1)]
head(NewData)
```

#4. Data Modeling
After we have standardized our entire dataset, we will split our dataset into training set as well as test set with a split ratio of 0.80. This means that 80% of our data will be attributed to the train_data whereas 20% will be attributed to the test data. We will then find the dimensions using the dim() function –

```{r}
library(caTools)
set.seed(123)
data_sample = sample.split(NewData$Class,SplitRatio=0.80)
train_data = subset(NewData,data_sample==TRUE)
test_data = subset(NewData,data_sample==FALSE)
dim(train_data)
dim(test_data)
```

#5. Fitting Logistic Regression Model
In this section of credit card fraud detection project, we will fit our first model. We will begin with logistic regression. A logistic regression is used for modeling the outcome probability of a class such as pass/fail, positive/negative and in our case – fraud/not fraud. We proceed to implement this model on our test data as follows –

```{r}
Logistic_Model=glm(Class~.,test_data,family=binomial())
summary(Logistic_Model)
```
After we have summarised our model, we will visual it through the following plots –

```{r}
plot(Logistic_Model)
```

In order to assess the performance of our model, we will delineate the ROC curve. ROC is also known as Receiver Optimistic Characteristics. For this, we will first import the ROC package and then plot our ROC curve to analyze its performance.

```{r}
library(pROC)
lr.predict <- predict(Logistic_Model,test_data, probability = TRUE)
auc.gbm = roc(test_data$Class, lr.predict, plot = TRUE, col = "blue")
```

#6. Fitting a Decision Tree Model
In this section, we will implement a decision tree algorithm. Decision Trees to plot the outcomes of a decision. These outcomes are basically a consequence through which we can conclude as to what class the object belongs to. We will now implement our decision tree model and will plot it using the rpart.plot() function. We will specifically use the recursive parting to plot the decision tree.
```{r}
library(rpart)
library(rpart.plot)
decisionTree_model <- rpart(Class ~ . , creditcard_data, method = 'class')
predicted_val <- predict(decisionTree_model, creditcard_data, type = 'class')
probability <- predict(decisionTree_model, creditcard_data, type = 'prob')
rpart.plot(decisionTree_model)
```

#7. Artificial Neural Network
Artificial Neural Networks are a type of machine learning algorithm that are modeled after the human nervous system. The ANN models are able to learn the patterns using the historical data and are able to perform classification on the input data. We import the neuralnet package that would allow us to implement our ANNs. Then we proceeded to plot it using the plot() function. Now, in the case of Artificial Neural Networks, there is a range of values that is between 1 and 0. We set a threshold as 0.5, that is, values above 0.5 will correspond to 1 and the rest will be 0. We implement this as follows –
```{r}
library(neuralnet)
ANN_model =neuralnet (Class~.,train_data,linear.output=FALSE)
plot(ANN_model)

predANN=compute(ANN_model,test_data)
resultANN=predANN$net.result
resultANN=ifelse(resultANN>0.5,1,0)
```

#8. Gradient Boosting (GBM)
Gradient Boosting is a popular machine learning algorithm that is used to perform classification and regression tasks. This model comprises of several underlying ensemble models like weak decision trees. These decision trees combine together to form a strong model of gradient boosting. We will implement gradient descent algorithm in our model as follows –
```{r}
library(gbm, quietly=TRUE)

# Get the time to train the GBM model
system.time(
       model_gbm <- gbm(Class ~ .
               , distribution = "bernoulli"
               , data = rbind(train_data, test_data)
               , n.trees = 500
               , interaction.depth = 3
               , n.minobsinnode = 100
               , shrinkage = 0.01
               , bag.fraction = 0.5
               , train.fraction = nrow(train_data) / (nrow(train_data) + nrow(test_data))
)
)

#Determine best iteration based on test data
gbm.iter = gbm.perf(model_gbm, method = "test")
```



```{r}
model.influence = relative.influence(model_gbm, n.trees = gbm.iter, sort. = TRUE)
#Plot the gbm model

plot(model_gbm)
```

```{r}
# Plot and calculate AUC on test data
gbm_test = predict(model_gbm, newdata = test_data, n.trees = gbm.iter)
gbm_auc = roc(test_data$Class, gbm_test, plot = TRUE, col = "red")
```

```{r}
print(gbm_auc)
```

